Architectures and Open pNets

### 2018-11-21 2018-Arch-pNets/arch-pNets.tex
pnets notations and properties

\noteLH{a pred is a g a post is a e}
The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes the actions of several holes, 
the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{defn:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes  and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {{\alpha}}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
        is an action of the hole $j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
	\assigns{\variables}$\ is 
	a set of assignments that are the effects of the transition.
Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\begin{multline}
\Pred_{\symb{sv}}(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
{\alpha'} {g}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\
\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
\alpha=\alpha' 
\land g
\end{multline}

@@

@@

\Fig{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
architecture, including the encodings of the two coordinators, \ie
$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.  Notice that the
encoding in the figure is slightly optimised: some of the ports do not
have an associated Boolean value, nor the additional loop transitions.
\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation once we have defined the
encoding of the interaction model.}

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
  \label{fig:FailureTimer:pNet}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{TimerOpenAut}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

12 open transitions... Comments on the predicates ???

Should list some temporal logic properties....

>>>>

\noteLH{a pred is a g a post is a u (modified macros!)}
\renewcommand{\Pred}{g}
\renewcommand{\Post}{u}
The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes the actions of several holes, 
the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{defn:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes  and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {{\alpha}}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
        is an action of the hole $j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
	\assigns{\variables}$\ is 
	a set of assignments that are the effects of the transition.
Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\begin{multline}
\Predsv(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
{\alpha'} {g}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\
\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
\alpha=\alpha' 
\land g
\end{multline}

@@

\todoLHin{add a paragraph about pnets properties and usage, here are a few points (to be completed and written up properly depending on what we need}

- pnets as a model for gcm components (behaviour, distributed systems, verification)

- used for finite model checking (with finite domains for parameters)

- smt framework for reasoning on infinite models

- a theory of pnets: composition properties , stong (and weak) bisim
	** extract a few useful composition theorems? **

@@

\Fig{enc:nopri} shows the encoding of the Failure Monitor
architecture, including the encodings of the two coordinators, \ie
$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.  Notice that the
encoding in the figure is slightly optimised: some of the ports do not
have an associated Boolean value, nor the additional loop transitions.
\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation once we have defined the
encoding of the interaction model.}

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
  \caption{The pNET encoding the Failure Monitor architecture (without the priority model)}
  \label{fig:FailureTimer:pNet}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{FailureTimerZonePNET}
  \caption{The pNET encoding the Failure Monitor architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}
